Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/computation.tex
Working on 3 (almost done)

\begin{figure}[t]
  \input{pointelscomptime.tikz}
  \caption{ \label{fig:meanvisibility-computationComplexity}Computation
    time of visibility as a function of the number of pointels. We
    compare the computation time of the naive breadth first visibility
    algorithm against our algorithm using intervals. We input the same
    maximal radius to both versions (10, 20, 30) and test it on 6
    different figures (goursat, torus, rcube, sphere9, leopold, d20)
    with various gridsteps, giving us figures with pointel amounts
    ranging from 520 to 390235.}
\end{figure}

\begin{figure}
  \input{mean-distance.tikz}
  \caption{  \label{fig:meanvisibility-gridstep}. Mean Visibility Distance as a Function of Grid Resolution}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \input{pointelscomptime.tikz}
  \caption{ \label{fig:meanvisibility-computationComplexity}Computation
    time of visibility as a function of the number of pointels. We
    compare the running time of the naive breadth first visibility
    algorithm against our algorithm using intervals. We input the same
    maximal radius to both versions (10, 20, 30) and test it on 6
    different figures (goursat, torus, rcube, sphere9, leopold,
    ``D20'') with various gridsteps, ($\#$ pointels ranging from 520
    to 390235.}
\end{figure}

\begin{figure}
  \centering
  \input{mean-distance.tikz}
  \caption{  \label{fig:meanvisibility-gridstep}. Mean distance of visibility as a function of the gridstep $h$.}
\end{figure}
